### 2016-03-21 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
Removed RTL methods and cited Kat. Other general edits before sending to Dave

**Figure 2** Cohort effects on early-life RTL in Seychelles warblers. **A** temporal variation RTL in major and minor cohorts, **B** tempoeral variation in adult population size, and **C** early-life RTL in relation to cohort-level variation in adult population size. Lines and shaded areas in **C** are fitted values and 95% confidence limits from general linear models.

**Figure 3** Factors affecting early-life RTL in Seychelles warblers. **A** Model averaged estimates and 95% confidence intervals for explanatory terms used in a linear mixed model with RTL as the response variable (see main text for details; TQ = territory quality). **B-D** early life RTL in relation to season (**B**),tarsus length (**C**) and sex (**D**). Lines and shaded areas in **D** are fitted values and 95% confidence limits from general linear models.

**Figure** Longitudinal telomere dynamics in juvenile Seychelles warblers. **A** Juvenile telomere length in relation to adult telomere length within individuals. **B** $\Delta$RTL in relation to the time between sampling events. Lines and shaded areas represent fitted values and 95% confidence limits from general linear models. Raw data have been ommited from **B** for the sake of clarity, but are plotted in Figure S1.

**Figure 5** Factors affecting $\Delta$RTL in juvenile Seychelles warblers. Model averaged estimates and 95% confidence intervals for explanatory terms used in a linear mixed model with $\Delta$RTL as the response variable (see main text for details; TQ = territory quality).

@@

Fig4A <- ggplot(temp,
       aes(x = RTL,
           y = RTL1)) +
  ylab('Adult RTL') + 
  xlab('Juvenile RTL') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top') +
  geom_point(col='grey')+
  stat_smooth(method = 'lm',col='darkgrey')+
  annotate('text',x = 0,y = 2.1,label = 'A')

@@

>>>>

**Figure 2** Cohort effects on early-life RTL in Seychelles warblers. **A** temporal variation RTL in major and minor cohorts, **B** temporal variation in adult population size, and **C** early-life RTL in relation to cohort-level variation in adult population size. Lines and shaded areas in **C** are fitted values and 95% confidence limits from general linear models.

**Figure 3** Factors affecting early-life RTL in Seychelles warblers. **A** Model averaged estimates and 95% confidence intervals for explanatory terms used in a linear mixed model with RTL as the response variable (see main text for details; TQ = territory quality). **B,C** Early-life RTL and age in relation to tarsus length (**B**) and sex (**C**). Lines and shaded areas in **B** are fitted values and 95% confidence limits from a general linear model.

**Figure 4** Longitudinal telomere dynamics in juvenile Seychelles warblers. **A** Juvenile telomere length in relation to adult telomere length measured in the same individual. **B** $\Delta$RTL in relation to the time between sampling events. Lines and shaded areas represent fitted values and 95% confidence limits from general linear models. Raw data have been ommited from **B** for the sake of clarity, but are plotted in Figure S1.

**Figure 5** Factors affecting $\Delta$RTL in juvenile Seychelles warblers. **A** Model averaged estimates and 95% confidence intervals for explanatory terms used in a linear mixed model with $\Delta$RTL as the response variable (see main text for details; TQ = territory quality). **B** $\Delta$RTL in relation to tarsus length and sex.

@@

Fig4A <- ggplot(temp,
       aes(x = RTL,
           y = RTL1,
           col=Ageclass)) +
  ylab('Adult RTL') + 
  xlab('Juvenile RTL') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top') +
  geom_point(col='grey')+
  stat_smooth(method = 'lm',col='darkgrey')+
  annotate('text',x = 0,y = 2.1,label = 'A')

@@

ggplot(juvseason9,aes(x = RTL,y = Lifespan,col = Season))+
  geom_point()+
  stat_smooth(method = 'lm')
